Price of Anarchy for Mean Field Games

### 2018-07-29 PoA.tex
removed notation for limits that are >1

%proposition b_2 \to 0
\begin{proposition}
	Assume assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA =: PoA^{b_2\to 0} > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} =: PoA^{b_2 \to 0} > 1.$
\end{proof}

% proposition b2 bar infinity
\begin{proposition}
	Assuming assumption \ref{assumption}, then:
	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
	Furthermore, if	$\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA =: PoA^{\bar{b}_2\to 0} > 1. 
	\end{equation*}	
	\label{prop:b2bar}
\end{proposition}

@@

	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	\begin{equation*}
	    0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} = \frac{1}{2}\int_0^T \left[q+\bar{q} + B^{\eta} \eta_t^2 \right] v_t dt + \frac{1}{2}(q_T + \bar{q}_T) v_T + \frac{1}{2}w^{\bar{b}_2 \to 0}_0 (\mathbb{E}(\xi))^2<\infty.     
	\end{equation*}
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} =: PoA^{\bar{b}_2 \to 0} > 1. $$
\end{proof}

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA =: PoA^{b_1 \to 0} > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA =: PoA^{\bar{b}_1 \to 0} > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$. Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} =: PoA^{b_1 \to 0} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1} =: PoA^{\bar{b}_1 \to 0} > 1$.\\

>>>>

%proposition b_2 \to 0
\begin{proposition}
	Assume assumption \ref{assumption}. If $\bar{b}_2= 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA = 1,
	\end{equation*}
	whereas if $\bar{b}_2 > 0$, then:
	\begin{equation*}
	\lim_{b_2 \to 0} PoA > 1.
	\end{equation*}
\label{prop:b2_to_0}
\end{proposition}

@@

	From equation (\ref{eq:v_t_new_notation}) and the bounded convergence theorem, for each $t \in [0,T]$:
	$$ \lim_{b_2 \to 0}v_t^{b_2}=Var(\xi) e^{2b_1 t} + \sigma^2 \int_0^t e^{2b_1 (t-s)} ds=:v_t^{b_2 \to 0}>0,$$
	and thus, $ 0 < \lim_{b_2 \to 0} SC^{MKV,b_2} < \infty.$ We conclude $\lim_{b_2 \to 0} PoA^{b_2} > 1.$
\end{proof}

% proposition b2 bar infinity
\begin{proposition}
	Assuming assumption \ref{assumption}, then:
	$$ \qquad\lim_{\bar{b}_2 \to \infty} PoA = 1.$$
	Furthermore, if	$\frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})} \neq \frac{q_T+\bar{q}_T(1-s_T)^2}{q_T+\bar{q}_T(1-s_T)}$ then:
	\begin{equation*}
	\lim_{\bar{b}_2 \to 0} PoA > 1. 
	\end{equation*}	
	\label{prop:b2bar}
\end{proposition}

@@

	Meanwhile, $\eta_t$ does not depend on $\bar{b}_2$, and therefore the variance $v_t$ also does not depend on $\bar{b}_2$. It is easy to check that $0<v_t<\infty$ for $t>0$ and $0 \leq w^{\bar{b}_2 \to 0}_0 < \infty$, and thus,
	$$ 0<\lim_{\bar{b}_2 \to 0}SC^{MKV,\bar{b}_2} <\infty.$$
	Hence, we deduce:
	$$ \lim_{\bar{b}_2 \to 0} PoA^{\bar{b}_2} > 1. $$
\end{proof}

@@

% proposition b1 and b1 bar
\begin{proposition}\label{prop:b1_b1bar}
	Assuming assumption \ref{assumption}, the initial condition satisfies $Var(\xi)>0$, and:
	\begin{equation*}
	\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot (q_T+\bar{q}_T(1-s_T)) \neq q_T+\bar{q}_T(1-s_T)^2,
	\end{equation*}
	then:
	\begin{equation*}
	\begin{split}
	    \lim_{b_1 \to 0} PoA > 1\qquad &\text{and} \qquad \lim_{\bar{b}_1 \to 0} PoA > 1,\\
	    \lim_{b_1 \to \infty} PoA = 1 \qquad &\text{and} \qquad\lim_{\bar{b}_1 \to \infty} PoA =\infty.
	\end{split}
	\end{equation*}
\end{proposition}
\begin{proof}
	\textbf{Cases 1 and 2:} First, we consider $b_1 \to 0$. We have $A^{u,b_1} \to A^{b_1\to 0}_u$, $\delta^{+,b_1}_u \to \delta^{+,b_1\to 0}_u>0$, and $\delta^{-,b_1}_u \to \delta^{-,b_1\to 0}_u<0$, and similarly for $A^{w,b_1}$, $A^{\eta,b_1}$, $\delta^{\pm,b_1}_w$, and $\delta^{\pm,b_1}_\eta$. Clearly we have for each $t\in[0,T]$, $\lim_{b_1 \to 0}u^{b_1}_t=:u^{b_1\to 0}_t$, $\lim_{b_1 \to 0}w^{b_1}_t=:w^{b_1 \to 0}_t$, and $\lim_{b_1 \to 0}\eta^{b_1}_t=:\eta^{b_1 \to 0}_t$. Next, we show that the three sequences are uniformly bounded. Let $0<\epsilon<-\delta^{-,b_1\to 0}_u$. There exists a $b_1^*$ such that $\max \left \{\left| \delta^{+,b_1}_u-\delta^{+,b_1\to0}_u \right|,\left| \delta^{-,b_1}_u-\delta^{-,b_1\to0}_u \right| \right\}<\epsilon$ for each $b_1 \leq b_1^*$. Then for each $b_1 \leq b_1^*$ and $t\in[0,T]$, we have:
	\begin{equation*}
		\left|u^{b_1}_t\right| \leq \frac{C^u+D^u\left(\delta^{+,b_1}_u-\delta^{-,b_1}_u\right) }{-\delta^{-,b_1}_u} \\
		\leq \frac{C^u+D^u\left(\delta^{+,b_1\to 0}_u-\delta^{-,b_1 \to 0}_u+2\epsilon\right) }{-\delta^{-,b_1\to 0}_u-\epsilon},
	\end{equation*}
	and similarly for $\left|w^{b_1}_t\right|$ and $\left|\eta^{b_1}_t\right|$. From the assumption $\frac{b_2}{b_2+\bar{b}_2}\cdot \frac{r + \bar{r}(1- \bar{s})^2}{r + \bar{r}(1-\bar{s})}\cdot q_T+\bar{q}_T(1-s_T) \neq q_T+\bar{q}_T(1-s_T)^2$, we have $D^{u} \neq D^{w}$ and thus by continuity, $u^{b_1\to 0}_t \neq w^{b_1\to 0}_t$ on a set of positive Lebesgue measure.

@@

	Therefore, by Proposition \ref{prop:diff_SC}, and the bounded convergence theorem, $0<\lim_{b_1 \to 0} \Delta SC^{b_1}<\infty$. By the bounded convergence theorem, $\lim_{b_1 \to 0}v^{b_1}_t=:v_t^{b_1 \to 0}$, which is bounded over $t\in [0,T]$, and thus $0<\lim_{b_1 \to 0} SC^{MKV,b_1}<\infty.$
    Therefore, $\lim_{b_1 \to 0} PoA^{b_1} > 1$. The proof can be repeated to show $\lim_{\bar{b}_1 \to 0} PoA^{\bar{b}_1}  > 1$.\\
